Placeholder

### 2021-02-09 Paper_Histograms.Rmd
Reformatted the gender and employ plots in the age, gender, ethnicity and employ retro figure

@@

gridExtra::grid.arrange(arranged_gender_plot, arranged_retro_age_plot, arranged_employ_plot,
          arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,
          layout_matrix = retro_matrix, nrow = 2)

>>>>

dat.retro_gender_male_female <- dat.retro_gender_distribution %>% 
  filter(Gender_collapsed != "Non-binary/Self-defined")

arranged_collapsed_gender_plot <- dat.retro_gender_male_female %>% 
  ggplot(aes(x = Gender_collapsed, y = n, fill = Sample_plot)) +
  geom_bar(position = "dodge", stat = "identity") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Participant Gender",
       y = "N participants") +
  theme(legend.position = "none") + 
  theme(legend.title = element_blank())

arranged_employ_plot <- dat.retro_employment_plot %>% 
  ggplot(aes(x = employment_prior_covid, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Employment status",
       y = "N participants") +
  theme(legend.position = "none") + 
  theme(legend.title = element_blank()) +
  scale_y_continuous(breaks = seq(0, 6000, by = 1000)) +
  scale_x_discrete(guide = guide_axis(n.dodge = 3),
                   expand = expansion(mult = c(0.2, 0.3)))

@@

gridExtra::grid.arrange(arranged_collapsed_gender_plot, arranged_retro_age_plot, arranged_employ_plot,
          arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,
          layout_matrix = retro_matrix, nrow = 2)
